Machine Learning Model for Agricultural Data Applications

### 2021-03-17 chapters/relatedWorks.tex
Intro-Abstract(100%)-Related Works(50%)
Related Works completed

\section{Data Science}
\todo{Create a Diagram and have my Question in the middle. From reading my first Journal paper, I'll add key branches to the diagram.}

\todo{In the diagram - Reader can identify - This is my Diagram - This is my Question and I have the relevant things properly cited and referenced. How to add citation to a diagram. }

@@

@@

Machine Learning itself is a subset of AI that focuses on teaching a machine how to do this without being explicitly programmed.

Deep Learning is a subset of Machine Learning which takes this idea even further. It allows us to automatically extract the useful pieces of information needed to inform these future predictions.

Availability of localized and external data can help to practice *Precision Agriculture*

Like all other neural networks, deep-learning models don't take as input raw text:
they only work with numeric tensors. Vectorizing text is the process of transforming text
into numeric tensors. This can be done in multiple ways

@@

According to this article by Usama Fayyad \cite{fayyad1996data} data mining is referred to  as the overall process of discovering useful information from data. William S. Cleveland, \cite{cleveland2001data}   who at that time was a Distinguished Member of Technical Staff in the Statistics Research Department at Bell Labs, Murray Hill, defined data science as it is used today. He did that by combining computer science with data mining. He made statistics a lot more technical because he believed it would expand the possibilities of data mining and produce a powerful force for innovation. Now, we can take advantage of computational power for statistics.

@@

\begin{figure}[h!]
	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{workflow.png}
	\caption{Machine Learning Workflow.}
	\label{fig:workflow}
\end{figure}

>>>>

@@

\section{Data Science}

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.75\textwidth, height=0.75\columnwidth]{Related_Works.png}
	\caption{Related Works.\protect\cite{tkacz2001neural, chuku2017intelligent, kiss2011significance, yamak2019comparison}}
	\label{fig:relatedWorks}
\end{figure}

@@

Machine Learning itself is a subset of AI that focuses on teaching a machine how to do this without being explicitly programmed. Deep Learning is a subset of Machine Learning which takes this idea even further. It allows us to automatically extract the useful pieces of information needed to inform these future predictions.

@@

Tkacz's \cite{tkacz2001neural} research analyzes the Canadian GDP growth rates. His results show that artificial neural networks are superior to linear models in yearly forecasting.
Chuku  and his colleagues \cite{chuku2017intelligent} examined GDP data from Kenya, Nigeria and South Africa. Their results also showed that artificial neural networks were superior to structural econometric models. They stated that these countries are \enquote{exposed to potential chaotic influences from commodity prices, external factors, and economic factors} \cite[p.25]{chuku2017intelligent}. Usama Fayyad \cite{fayyad1996data} referred to data mining as the overall process of discovering useful information from data. William S. Cleveland, \cite{cleveland2001data} who at that time was a Distinguished Member of the Technical Staff in the Statistics Research Department at Bell Labs, Murray Hill, defined data science as it is used today. He did that by combining computer science with data mining. He made statistics a lot more technical because he believed it would expand the possibilities of data mining and produce a powerful force for innovation. Now, we can take advantage of computational power for statistics.

@@

\begin{figure}[h!]
	\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{workflow.png}
	\caption{Machine Learning Workflow.\protect\cite{division_2000, charfeddine2020reviewing, krose1993introduction}}
	\label{fig:workflow}
\end{figure}
